---
title: "BSS Dep Man"
author: "LAURA PAABY"
date: "2023-05-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
pacman::p_load(tidyverse, readxl, lme4)

### read data:
data <- read_excel("data/XL_Diary_study_merged_data.xlsx")

#### used to display that 
data %>% 
  filter(SurveyID == 264)

```


```{r}
data %>% 
  group_by(SurveyID) %>% 
  summarise(n()) # three missing ... 

# removing missing MAYBE THIS INSTEAD SHOULD BE RENAMED DUNNO
data %>% 
  filter(SurveyID == "missing")

data1 <- data %>% 
  filter(SurveyID != "missing")

# checking
data1 %>% 
  group_by(SurveyID) %>% 
  summarise(n())

raw_data <- data1
head(raw_data)

```
Cons_1 ==> consensus, I would argue that people without consensus should be deleted. 

GOTTA BE OBS HERE - NEED TO BE MATCHABLE WITH BASELINE 

survey id has a *missing* I'll just turn into 0 ==> I assume that this are AK and Maries testers 
survey id has a *new* I'll just turn into 1
```{r}
#raw_data$SurveyID <- ifelse(raw_data$SurveyID == "missing", "0", raw_data$SurveyID )
raw_data$SurveyID <- ifelse(raw_data$SurveyID == "new", "1", raw_data$SurveyID )
unique(raw_data$SurveyID)
unique(data$SurveyID)


raw_data$SurveyID <- as.factor(raw_data$SurveyID)
```

# FILTER EACH QUESTION 
```{r}
data_names <- raw_data %>% 
  rename(consensus = cons_1)

# wb hap == level of happiness at work (1-7)
wb_hap <- raw_data %>% 
  select(starts_with("wb_hap"), "SurveyID")

# wb so == level of social engagement (1-7)
wb_so <- raw_data %>% 
  select(starts_with("wb_so"), "SurveyID")

# wb so == level of helbred (1-7)
wb_he <- raw_data %>% 
  select(starts_with("wb_he"), "SurveyID")

# wb so == PRESENTEISM (Har du arbejdet i dag, selv om du ikke følte dig frisk nok til at arbejde?)
# NEJ = 1, Ja = antal i S6
presenteism <- raw_data %>% 
  select(starts_with("pre"), "SurveyID") %>% 
  mutate_if(is.character, as.numeric) ### for some reason they arent all numeric:
presenteism$SurveyID <- as.character(presenteism$SurveyID)

S6_pres <- raw_data %>% 
  select(starts_with("s_6"), "SurveyID") %>% 
  mutate_if(is.character, as.numeric) ### for some reason they arent all numeric:
S6_pres$SurveyID <- as.character(S6_pres$SurveyID)


# wb so == level of absense that you should have done (1-5) - 1 = hele tiden, 5 = slet ikke.  
#(Har du i dag tænkt på at du burde have været hjemme i stedet for på arbejde?)
absense <- raw_data %>% 
  select(starts_with("abs"), "SurveyID")

# contact with leader today (1 ja fysisk, 2, ja digitalt, 3 nej)
contact <- raw_data %>% 
  select(starts_with("cont"), "SurveyID")

# satisfaction with leader today (1-5)
sat <- raw_data %>% 
  select(starts_with("sat"), "SurveyID")

# ask help from leader today (1-5), 1 is very agree, 5 is very disagree 
ls_1 <- raw_data %>% 
  select(starts_with("ls_1"), "SurveyID")

# count on leader today (1-5) 1 is very agree, 5 is very disagree 
ls_2 <- raw_data %>% 
  select(starts_with("ls_2"), "SurveyID")


# acknowledgement from leader today (1-5) 1 is very agree, 5 is very disagree 
ls_3 <- raw_data %>% 
  select(starts_with("ls_3"), "SurveyID")


# event (pos or neg) with leader today (1 yes, 2 no, 3 neither nor) 
event <- raw_data %>% 
  select(!starts_with("ev_1_")) %>% 
  select(starts_with("ev"), "SurveyID")

# evaluation and comment:
evaluation <- raw_data %>% 
  select(starts_with("ev_1_"), "SurveyID")

```



# FIX WIDE FORMAT
```{r}
###### MAKING ALL LONG FORMAT: ##### 
abs_long <- absense %>%
  pivot_longer(!SurveyID, names_to = "absense_var", values_to = "Absense_Score")

contact_long <- contact %>%
  pivot_longer(!SurveyID, names_to = "cont_var", values_to = "Contact_Score")

eval_long <- evaluation %>%
  pivot_longer(!SurveyID, names_to = "eval_var", values_to = "eval_Score")

event_long <- event %>%
  pivot_longer(!SurveyID, names_to = "event_var", values_to = "event_Score")

ls1_long <- ls_1 %>%
  pivot_longer(!SurveyID, names_to = "ls1_var", values_to = "ls1_Score")

ls2_long <- ls_2 %>%
  pivot_longer(!SurveyID, names_to = "ls2_var", values_to = "ls2_Score")

ls3_long <- ls_3 %>%
  pivot_longer(!SurveyID, names_to = "ls3_var", values_to = "ls3_Score")

presenteism_long <- presenteism %>%
  pivot_longer(!SurveyID, names_to = "present_var", values_to = "present_Score")

s6_long <- S6_pres %>%
  pivot_longer(!SurveyID, names_to = "s6_var", values_to = "s6_Score")

sat_long <- sat %>%
  pivot_longer(!SurveyID, names_to = "sat_var", values_to = "sat_Score")

wb_hap_long <- wb_hap %>%
  pivot_longer(!SurveyID, names_to = "wb_hap_var", values_to = "wb_hap_Score")

wb_he_long <- wb_he %>%
  pivot_longer(!SurveyID, names_to = "wb_he_var", values_to = "wb_he_Score")

wb_so_long <- wb_so %>%
  pivot_longer(!SurveyID, names_to = "wb_so_var", values_to = "wb_so_Score")
```



##### time column fix 
```{r}
#### function to fix time:
add_time_column <- function(data, var_prefix, abs_var) {
  data$time <- NA
  for (i in 1:26) {
    var_name <- paste0(var_prefix, i)
    data$time <- ifelse(grepl(var_name, abs_var), i, data$time)
  }
  return(data)
}

### using on all dfs:
abs_long <- add_time_column(abs_long, "abs_", abs_long$absense_var)
contact_long <- add_time_column(contact_long, "cont_", contact_long$cont_var)
eval_long <- add_time_column(eval_long, "ev_1_", eval_long$eval_var)
event_long <- add_time_column(event_long, "ev_", event_long$event_var) #### FIKS DAG 25

ls1_long <- add_time_column(ls1_long, "ls_1_d", ls1_long$ls1_var)
ls2_long <- add_time_column(ls2_long, "ls_2_d", ls2_long$ls2_var)
ls3_long <- add_time_column(ls3_long, "ls_3_d", ls3_long$ls3_var)


presenteism_long <- add_time_column(presenteism_long, "pre_d", presenteism_long$present_var)
s6_long <- add_time_column(s6_long, "s_6_d", s6_long$s6_var)

sat_long <- add_time_column(sat_long, "sat_", sat_long$sat_var)


wb_hap_long <- add_time_column(wb_hap_long, "wb_hap_d", wb_hap_long$wb_hap_var)
wb_he_long <- add_time_column(wb_he_long, "wb_he_d", wb_he_long$wb_he_var)
wb_so_long <- add_time_column(wb_so_long, "wb_so_d", wb_so_long$wb_so_var)
```

first just fixing day 25 in event:
```{r}
event_long$time <- event_long$time %>%
  replace_na(25)

```



#### COMBINING ALL DATA: 
this way takes for ever dunno why
```{r}
# create a list of 10 data frames
# didn't use but nice for overview 
dfs <- list(abs_long, contact_long, eval_long, event_long, ls1_long, ls2_long, ls3_long, presenteism_long, s6_long, sat_long, wb_hap_long, wb_he_long, wb_so_long)

# perform an inner join on the "time" and "ID" variables
merged1 <- inner_join(abs_long, contact_long, by = c("time" = "time", "SurveyID" = "SurveyID"))
merged2 <- inner_join(merged1, eval_long, by = c("time" = "time", "SurveyID" = "SurveyID"))
merged3 <- inner_join(merged2, event_long, by = c("time" = "time", "SurveyID" = "SurveyID"))
merged4 <- inner_join(merged3, ls1_long, by = c("time" = "time", "SurveyID" = "SurveyID"))
merged5 <- inner_join(merged4, ls2_long, by = c("time" = "time", "SurveyID" = "SurveyID"))
merged6 <- inner_join(merged5, ls3_long, by = c("time" = "time", "SurveyID" = "SurveyID"))
merged7 <- inner_join(merged6, presenteism_long, by = c("time" = "time", "SurveyID" = "SurveyID"))
merged8 <- inner_join(merged7, s6_long, by = c("time" = "time", "SurveyID" = "SurveyID"))
merged9 <- inner_join(merged8, sat_long, by = c("time" = "time", "SurveyID" = "SurveyID"))
merged10 <- inner_join(merged9, wb_hap_long, by = c("time" = "time", "SurveyID" = "SurveyID"))
merged11 <- inner_join(merged10, wb_he_long, by = c("time" = "time", "SurveyID" = "SurveyID"))
merged12 <- inner_join(merged11, wb_so_long, by = c("time" = "time", "SurveyID" = "SurveyID"))

# view the merged data frame
final_long_df <- merged12 %>%
  select(!ends_with("var")) 

final_long_df %>% 
  group_by(SurveyID) %>% 
  summarise(n()) 

final_long_df <- final_long_df %>%
  rename(Day = time, 
         eval_comment = eval_Score) %>% 
  select(Day, SurveyID, everything())

### DUMMY CODING SICKNESS 
final_long_df$day_off <- ifelse(final_long_df$Absense_Score == 96, 1, 0)
final_long_df$sickness <- ifelse(final_long_df$Absense_Score == 97, 1, 0)
final_long_df$absent_oth_reason <- ifelse(final_long_df$Absense_Score == 98, 1, 0)
final_long_df$miss_ans <- ifelse(final_long_df$Absense_Score == 99, 1, 0)

```
# svarrate count:
(hvis 91 er med:)
```{r}
dat_count_somewhat <- final_long_df %>%
  filter(!is.na(Absense_Score) == T | !is.na(ls1_Score) == T | !is.na(ls2_Score) == T | !is.na(ls3_Score) == T |!is.na(event_Score) == T | !is.na(present_Score) == T | !is.na(sat_Score) == T | !is.na(wb_hap_Score) == T | !is.na(wb_he_Score) == T | !is.na(wb_so_Score) == T) %>% 
  filter(!Absense_Score == 99 | !ls1_Score == 99 | !ls2_Score == 99 | !ls3_Score == 99 | !event_Score == 99| !present_Score == 99 | !sat_Score == 99 | !wb_hap_Score == 99 | !wb_he_Score == 99 | !wb_so_Score == 99)

dat_count_complete <- final_long_df %>%
  filter(!is.na(Absense_Score) == T & !is.na(ls1_Score) == T & !is.na(ls2_Score) == T & !is.na(ls3_Score) == T &!is.na(event_Score) == T & !is.na(present_Score) == T & !is.na(sat_Score) == T & !is.na(wb_hap_Score) == T & !is.na(wb_he_Score) == T & !is.na(wb_so_Score) == T) %>% 
   filter(!Absense_Score == 99 & !ls1_Score == 99 & !ls2_Score == 99 & !ls3_Score == 99 & !event_Score == 99 & !present_Score == 99 &  !sat_Score == 99 & !wb_hap_Score == 99 & !wb_he_Score == 99 & !wb_so_Score == 99)

length(dat_count_somewhat$Absense_Score)
length(dat_count_complete$Absense_Score)
length(final_long_df$Absense_Score)
```

This means: *988* surveys was sent out across the entire period, *864* was at least somewhat answered to, and *818* was fully completed. 

# Fix 91
i code 91 as NA, cause NA rows will be removed later on, but this makes the merging a lot easier. 
```{r}
final_long_df[final_long_df == 91] <- NA

### now no 91 but NAs instead 
final_long_df %>% 
  ggplot(aes(x = Day)) + 
  geom_bar(position = "dodge") +
  facet_wrap(~ Absense_Score) +
  labs(x = "Day", 
       y = "Frequency of Observations",
       title= "Absense Score") +
  scale_fill_brewer(palette = "Blues") +
  geom_text(stat='count', aes(label=..count..), vjust=-0.5, size = 1.8) +
  theme_bw()

dat_clean <- final_long_df

#write_csv(dat_clean, "/Users/laura/Desktop/work_bss/data/clean_survey_data.csv")
```
# svarrate count:
nu hvis 91 er considered NA:
```{r}
dat_count_somewhat <- final_long_df %>%
  filter(!is.na(Absense_Score) == T | !is.na(ls1_Score) == T | !is.na(ls2_Score) == T | !is.na(ls3_Score) == T |!is.na(event_Score) == T | !is.na(present_Score) == T | !is.na(sat_Score) == T | !is.na(wb_hap_Score) == T | !is.na(wb_he_Score) == T | !is.na(wb_so_Score) == T) %>% 
  filter(!Absense_Score == 99 | !ls1_Score == 99 | !ls2_Score == 99 | !ls3_Score == 99 | !event_Score == 99| !present_Score == 99 | !sat_Score == 99 | !wb_hap_Score == 99 | !wb_he_Score == 99 | !wb_so_Score == 99)

dat_count_complete <- final_long_df %>%
  filter(!is.na(Absense_Score) == T & !is.na(ls1_Score) == T & !is.na(ls2_Score) == T & !is.na(ls3_Score) == T &!is.na(event_Score) == T & !is.na(present_Score) == T & !is.na(sat_Score) == T & !is.na(wb_hap_Score) == T & !is.na(wb_he_Score) == T & !is.na(wb_so_Score) == T) %>% 
   filter(!Absense_Score == 99 & !ls1_Score == 99 & !ls2_Score == 99 & !ls3_Score == 99 & !event_Score == 99 & !present_Score == 99 &  !sat_Score == 99 & !wb_hap_Score == 99 & !wb_he_Score == 99 & !wb_so_Score == 99)

length(dat_count_somewhat$Absense_Score)
length(dat_count_complete$Absense_Score)
length(final_long_df$Absense_Score)
```




get it back in to work with :D 
```{r}
long_dat <- read_csv("data/clean_survey_data.csv")
```




# BASELINE DATA 
for employees ==> a lot of cleaning needs to be done, but not sure how as I don't know how the data was collected. 

There seem to be some kind of indicator of whether or not they have completed (statoverall), but this is not in the data provided.


```{r}
baseline_raw <- read_excel("/Users/laura/Desktop/work_bss/Baseline_Raw data_employees/csv/baseline_employees_dataset.xlsx")

# remove empty rows
baseline_df <- baseline_raw %>% 
  drop_na(cons, id) %>% 
  arrange(id)

# remove duplicated ids (the duplicated row is empty anyway) 
dup_list <- which(duplicated(baseline_df$id))
dup_list

baseline_df[38:48,]


# way to clean by index
clean_baseline <- baseline_df %>%  
  filter(!row_number() %in% c(2, 7,9,14,17,19, 20, 21, 25, 28,30,32,33,36,38,39, 40, 41, 42, 43, 44, 45, 47, 48, 50,52,53)) %>% 
  filter(!id %in% c(0, 233))

length(unique(clean_baseline$id)) # 33 ids now 
which(duplicated(clean_baseline$id)) # 0 


#can be done by only choosing those who completed *statoverall_4 == 1* meaning fully completed, but then I only have 30 ids. Gives the same vupsi. But now I now the iDs 

baseline_no_dup <- baseline_df %>% 
  filter(statoverall_4 == 1) # choosing only complete surveys
```

Hvorfor forskellige ids?
- de kommer løbende i form af nye ansættelser eller stopper i forløbet, så nogle har kun nået baseline og er så stoppet, mens andre er kommet lidt senere og har derfor ikke gennemført baseline. 
```{r}

# SUMMARIZING IDS 
id_clean <- clean_baseline %>% 
  select(id) %>% 
  group_by(id) %>% 
  arrange()

surv_ids <- as.data.frame(unique(long_dat$SurveyID)) %>% 
  rename(SurveyID = "unique(long_dat$SurveyID)") %>% 
  arrange(SurveyID)


# CHECKING IF MATCH   
id_clean$id %in% surv_ids$SurveyID
id_clean$id[20:21] ### 209 ID does not have a survey, but a baseline 

surv_ids$SurveyID %in% id_clean$id

surv_ids$SurveyID[c(1,16,19,20,24,28,29,30,31)]  # indexed by the rows in FALSE above 
```

The ID's with no baseline is therefore: 
*1 189 209 211 237 255 258 264 266* remember that 1 is the SurveyID initially called `new`. 

The IDs only with baseline is: 
*236 243*
(236 is the transgender)


```{r}
# I choose the Survey data only with the IDs represented in both:
df_small <- long_dat %>% 
  filter(SurveyID %in% id_clean$id)

length(unique(df_small$SurveyID)) # 29 IDS now 


baseline_small <- clean_baseline %>% 
  filter(id %in% df_small$SurveyID)

length(unique(baseline_small$id))

# checking its the same ids 
unique(df_small$SurveyID %in% baseline_small$id)

# renaming to make merge easier
baseline_small <- baseline_small %>% 
  rename(SurveyID = id)
```



## Making baseline data long format 
```{r}
# making list of days to get baseline on long format 
dat <- data.frame(matrix(nrow = 26))
dat$Day <- c(1:26)
dat <- dat %>% 
  select(Day)

test_dat <- baseline_small %>% 
  select(cons, SurveyID, age, gen)

baseline_small_longformat <- merge(dat, baseline_small)

# now they are both on long format w 26 days and 29 ids 
dim(baseline_small_longformat)
dim(df_small)
```

## merging baseline and survey dat 
```{r}
final_clean_long_merged <- inner_join(df_small, baseline_small_longformat, by = c("Day" = "Day", "SurveyID" = "SurveyID"))

final_clean_long_merged <- final_clean_long_merged %>% 
  select(!cons) #removing consensus col 

#write_csv(final_clean_long_merged, "/Users/laura/Desktop/work_bss/data/all_data_merged.csv")
```



### Baseline EMOTIONS 
```{r}
emo_dat <- final_clean_long_merged %>% 
  select(Day, SurveyID, Absense_Score, present_Score, s6_Score, sat_Score, gen, age, ten_1, starts_with("emo"))

emo_dat$fix_s6_score <- ifelse(emo_dat$s6_Score > 50, NA, emo_dat$s6_Score)
emo_dat$fix_abs_score <- ifelse(emo_dat$Absense_Score > 50, NA, emo_dat$Absense_Score)
emo_dat$fix_pres_Score <- ifelse(emo_dat$present_Score > 50, NA, emo_dat$present_Score)
emo_dat$fix_sat_Score <- ifelse(emo_dat$sat_Score > 50, NA, emo_dat$sat_Score)

emo_dat_2 <- emo_dat %>% 
  group_by(Day, SurveyID, fix_abs_score, fix_pres_Score, gen, age, ten_1, s6_Score, fix_sat_Score) %>% 
  summarize(avr_sens = (sum(emo_1, emo_2, emo_3, emo_4, emo_5, emo_8)/6), 
            avr_insens = (sum(emo_6, emo_7, emo_9, emo_10)/4))


write_csv(emo_dat, "/Users/laura/Desktop/work_bss/data/emo_dat_all.csv")
write_csv(emo_dat_2, "/Users/laura/Desktop/work_bss/data/emo_average_dat.csv")
```
Okay so I have summarized all the emotions variable into two: the sensitive one (1,2,3,4,5,8) and the insensitive one (6,7,9,10). So if you report high on average in the sensitive one, it is because you are agreeing with statements that indicates you are sensitive and vice versa. 





# Model Data 
For now only making of the sat, abs, presenteeism and leadership variables. Does not make sense to make with the sickness yet, as only two observations. 
```{r}
data <- final_clean_long_merged
```

## Absenteeism 
#### abseenteism and satisfaction  
```{r}
filter_dat <- data %>% 
  select(Day, SurveyID, Absense_Score, sat_Score, age, gen, ten_1)

# filtering away all 98,99 etc. 
filter_dat$fix_sat_score <- ifelse(filter_dat$sat_Score > 10, NA, filter_dat$sat_Score)
filter_dat$fix_abs_score <- ifelse(filter_dat$Absense_Score > 10, NA, filter_dat$Absense_Score)

# removing day if both sat and abs are NA
filter_no_na <- filter_dat %>% 
  filter(!(is.na(fix_abs_score) == TRUE) | !(is.na(fix_sat_score) == TRUE)) %>% 
  select(Day, SurveyID, fix_sat_score, fix_abs_score, age, gen, ten_1)

# checking the data 
filter_no_na %>% 
  group_by(SurveyID) %>% 
  summarise(n())

# removing IDs observed less than 5 times:
model_dat_sat_abs <- filter_no_na %>% 
  filter(SurveyID != 147 & SurveyID != 232)

# trying model of this data 
#mod_test <- lmer(fix_abs_score ~ fix_sat_score + age + ten_1 + gen +(1|Day) + (1|SurveyID), model_dat_sat_abs)
#mod_test2 <- lmer(fix_abs_score ~ fix_sat_score + age + ten_1 + gen + (1|Day) + (1|SurveyID), model_dat_sat_abs)

# writing out csv 
#write_csv(model_dat_sat_abs, "/Users/laura/Desktop/work_bss/data/sat_abs_data.csv")


```


#### abseenteism, presenteeism and leadership variables 

```{r}
leader_dat <- data %>% 
  select(Day, SurveyID, Absense_Score, sat_Score, present_Score, ls1_Score, ls2_Score, ls3_Score, s6_Score, age, gen, ten_1)

# replacing all 98,99 etc. with NA 
leader_dat$fix_abs_score <- ifelse(leader_dat$Absense_Score > 10, NA, leader_dat$Absense_Score)
leader_dat$fix_ls1_score <- ifelse(leader_dat$ls1_Score > 10, NA, leader_dat$ls1_Score)
leader_dat$fix_ls2_score <- ifelse(leader_dat$ls2_Score > 10, NA, leader_dat$ls2_Score)
leader_dat$fix_ls3_score <- ifelse(leader_dat$ls3_Score > 10, NA, leader_dat$ls3_Score)
leader_dat$fix_pres_score <- ifelse(leader_dat$present_Score > 10, NA, leader_dat$present_Score)
leader_dat$fix_sat_score <- ifelse(leader_dat$sat_Score > 10, NA, leader_dat$sat_Score)


####################### DEALING W NA'S IN LEADER VARIBALES   ####################### 
## REMOVING SUBJECTS w no answers in leadership variables 

# Get unique IDs
unique_ids <- unique(leader_dat$SurveyID)

# Create a vector to store IDs to be removed
ids_to_remove <- c()

# Loop through unique IDs
for (id in unique_ids) {
  # Subset the data frame for the current ID
  id_rows <- leader_dat[leader_dat$SurveyID == id, ]
  
  # Check if all specified columns are NA for the current ID
  if (all(is.na(id_rows$fix_ls1_score)) && all(is.na(id_rows$fix_ls3_score)) && all(is.na(id_rows$fix_ls3_score))) {
    # Add the ID to the vector of IDs to be removed
    ids_to_remove <- c(ids_to_remove, id)
  }
}

ids_to_remove

# Remove rows corresponding to IDs in the vector
leader_dat <- leader_dat[!leader_dat$SurveyID %in% ids_to_remove, ]

lead_df_s6 <- leader_dat


##### removing THE DAYS if all are NA
leader_dat_no_na <- leader_dat %>% 
  filter(!(is.na(fix_abs_score) == TRUE) | (!(is.na(fix_pres_score) == TRUE) | !(is.na(fix_sat_score) == TRUE) | !(is.na(fix_ls1_score) == TRUE | !(is.na(fix_ls2_score) == TRUE | !(is.na(fix_ls2_score) == TRUE))))) 


leader_dat_no_na <- leader_dat_no_na %>% 
  select(!Absense_Score, !ls1_Score, !ls2_Score, !ls3_Score, !present_Score, !sat_Score) %>% 
  filter(SurveyID != 147 & SurveyID != 232)

# checking the data 
leader_dat_no_na %>% 
  group_by(s6_Score) %>% 
  summarise(n())

length(unique(leader_dat_no_na$SurveyID))


#write_csv(lead_df_s6, "/Users/laura/Desktop/work_bss/data/ls_s6_data.csv")
```



## Presenteeism
#### presenteeism and satisfaction 
```{r}
filter_dat_pres <- data %>% 
  select(Day, SurveyID, present_Score, sat_Score, age, gen, ten_1)

# filtering away all 98,99 etc. 
filter_dat_pres$fix_sat_score <- ifelse(filter_dat_pres$sat_Score > 10, NA, filter_dat_pres$sat_Score)
filter_dat_pres$fix_pres_score <- ifelse(filter_dat_pres$present_Score > 10, NA, filter_dat_pres$present_Score)

# removing day if both sat and abs are NA
filter_no_na_pres <- filter_dat_pres %>% 
  filter(!(is.na(fix_pres_score) == TRUE) | !(is.na(fix_sat_score) == TRUE)) %>% 
  select(Day, SurveyID, fix_sat_score, fix_pres_score, age, gen, ten_1)

# checking the data 
filter_no_na_pres %>% 
  group_by(SurveyID) %>% 
  summarise(n())

# removing IDs observed less than 5 times:
model_dat_sat_pres <- filter_no_na_pres %>% 
  filter(SurveyID != 147 & SurveyID != 232)

# trying model of this data 
#mod_test <- lmer(fix_abs_score ~ fix_sat_score + age + ten_1 + gen +(1|Day) + (1|SurveyID), model_dat_sat_abs)
#mod_test2 <- lmer(fix_abs_score ~ fix_sat_score + age + ten_1 + gen + (1|Day) + (1|SurveyID), model_dat_sat_abs)

# writing out csv 
#write_csv(model_dat_sat_pres, "/Users/laura/Desktop/work_bss/data/sat_pres_data.csv")

```




# LEADER DATA

```{r}
lead_dat <- read_excel("/Users/laura/Desktop/work_bss/Masterfile_2_Leader.xlsx")

colnames(lead_dat)

colnames(raw_data)

lead_dat$abs_6
```

```{r}
# wb hap == level of happiness at work (1-7)
wb_hap_lead <- lead_dat %>% 
  select(starts_with("wb_hap"), "SurveyID")

# wb so == level of social engagement (1-7)
wb_so_lead <- lead_dat %>% 
  select(starts_with("wb_so"), "SurveyID")

# wb so == level of helbred (1-7)
wb_he_lead <- lead_dat %>% 
  select(starts_with("wb_he"), "SurveyID")

# wb so == PRESENTEISM (Har du arbejdet i dag, selv om du ikke følte dig frisk nok til at arbejde?)
# NEJ = 1, Ja = antal i S6
presenteism_lead <- lead_dat %>% 
  select(starts_with("pre"), "SurveyID") 

S6_pres_lead <- lead_dat %>% 
  select(starts_with("s_6"), "SurveyID")


###### ABSENTEISM ###### 
###### her har vi 5 forskellige absense for some reason 
abs1 <- lead_dat %>% 
  select(starts_with("abs_1"), "SurveyID")

abs2 <- lead_dat %>% 
  select(starts_with("abs_2"), "SurveyID")

abs3 <- lead_dat %>% 
  select(starts_with("abs_3"), "SurveyID")

abs4 <- lead_dat %>% 
  select(starts_with("abs_4"), "SurveyID")

abs5 <- lead_dat %>% 
  select(starts_with("abs_5"), "SurveyID")


###### ES

es1 <- lead_dat %>% 
  select(starts_with("es_1"), "SurveyID")

es2 <- lead_dat %>% 
  select(starts_with("es_2"), "SurveyID")

es3 <- lead_dat %>% 
  select(starts_with("es_3"), "SurveyID")

```


```{r}
###### MAKING ALL LONG FORMAT: ##### 
# absense:
abs_long1 <- abs1 %>%
  pivot_longer(!SurveyID, names_to = "abs1_var", values_to = "abs1_score")

abs_long2 <- abs2 %>%
  pivot_longer(!SurveyID, names_to = "abs2_var", values_to = "abs2_score")

abs_long3 <- abs3 %>%
  pivot_longer(!SurveyID, names_to = "abs3_var", values_to = "abs3_score")

abs_long4 <- abs4 %>%
  pivot_longer(!SurveyID, names_to = "abs4_var", values_to = "abs4_score")

abs_long5 <- abs5 %>%
  pivot_longer(!SurveyID, names_to = "abs5_var", values_to = "abs5_score")


# presenteiism and how much
presenteism_long_lead <- presenteism_lead %>%
  pivot_longer(!SurveyID, names_to = "present_var", values_to = "present_Score")

s6_long_lead <- S6_pres_lead %>%
  pivot_longer(!SurveyID, names_to = "s6_var", values_to = "s6_Score")


# well being
wb_hap_long_lead <- wb_hap_lead %>%
  pivot_longer(!SurveyID, names_to = "wb_hap_var", values_to = "wb_hap_Score")

wb_he_long_lead <- wb_he_lead %>%
  pivot_longer(!SurveyID, names_to = "wb_he_var", values_to = "wb_he_Score")

wb_so_long_lead <- wb_so_lead %>%
  pivot_longer(!SurveyID, names_to = "wb_so_var", values_to = "wb_so_Score")


# es 
es1_long <- es1 %>%
  pivot_longer(!SurveyID, names_to = "es1_var", values_to = "es_1_Score")

es2_long <- es2 %>%
  pivot_longer(!SurveyID, names_to = "es2_var", values_to = "es_2_Score")

es3_long <- es3 %>%
  pivot_longer(!SurveyID, names_to = "es3_var", values_to = "es_3_Score")
```


#### fixing the time column on all:
```{r}
### TIME ON ABS
abs_long1 <- add_time_column(abs_long1, "abs_1_d", abs_long1$abs1_var)
abs_long2 <- add_time_column(abs_long2, "abs_2_d", abs_long2$abs2_var)
abs_long3 <- add_time_column(abs_long3, "abs_3_d", abs_long3$abs3_var)
abs_long4 <- add_time_column(abs_long4, "abs_4_d", abs_long4$abs4_var)
abs_long5 <- add_time_column(abs_long5, "abs_5_d", abs_long5$abs5_var)

### TIME ON WELLBEING 
wb_hap_long_lead <- add_time_column(wb_hap_long_lead, "wb_hap_d", wb_hap_long_lead$wb_hap_var)
wb_he_long_lead <- add_time_column(wb_he_long_lead, "wb_he_d", wb_he_long_lead$wb_he_var)
wb_so_long_lead <- add_time_column(wb_so_long_lead, "wb_so_d", wb_so_long_lead$wb_so_var)

### TIME ON WELLBEING 
es1_long <- add_time_column(es1_long, "es_1_d", es1_long$es1_var)
es2_long <- add_time_column(es2_long, "es_2_d", es2_long$es2_var)
es3_long <- add_time_column(es3_long, "es_3_d", es3_long$es3_var)

#### pres and s6
presenteism_long_lead <- add_time_column(presenteism_long_lead, "pre_d", presenteism_long_lead$present_var)
s6_long_lead <- add_time_column(s6_long_lead, "s_6_d", s6_long_lead$s6_var)
```

#### merging long dfs:
```{r}
# perform an inner join on the "time" and "ID" variables
merged1 <- inner_join(abs_long1, abs_long2, by = c("time" = "time", "SurveyID" = "SurveyID"))
merged2 <- inner_join(merged1, abs_long3, by = c("time" = "time", "SurveyID" = "SurveyID"))
merged3 <- inner_join(merged2, abs_long4, by = c("time" = "time", "SurveyID" = "SurveyID"))
merged4 <- inner_join(merged3, abs_long5, by = c("time" = "time", "SurveyID" = "SurveyID"))
merged5 <- inner_join(merged4, wb_hap_long_lead, by = c("time" = "time", "SurveyID" = "SurveyID"))
merged6 <- inner_join(merged5, wb_he_long_lead, by = c("time" = "time", "SurveyID" = "SurveyID"))
merged7 <- inner_join(merged6, wb_so_long_lead, by = c("time" = "time", "SurveyID" = "SurveyID"))
merged8 <- inner_join(merged7, es1_long, by = c("time" = "time", "SurveyID" = "SurveyID"))
merged9 <- inner_join(merged8, es2_long, by = c("time" = "time", "SurveyID" = "SurveyID"))
merged10 <- inner_join(merged9, es3_long, by = c("time" = "time", "SurveyID" = "SurveyID"))
merged11 <- inner_join(merged10, presenteism_long_lead, by = c("time" = "time", "SurveyID" = "SurveyID"))
merged12 <- inner_join(merged11, s6_long_lead, by = c("time" = "time", "SurveyID" = "SurveyID"))

# view the merged data frame
leader_long_df <- merged12 %>%
  select(!ends_with("var")) %>% 
  rename(Day = time) %>% 
  select(Day, SurveyID, everything()) 

leader_long_df <- leader_long_df %>% 
  select(!c(abs1_score, abs2_score, abs3_score, abs4_score))

#write_csv(leader_long_df, "/Users/laura/Desktop/work_bss/data/leader_survey_data.csv")
```

Okay ift absententiism og lederen her: 
- alle fem abs variabler er dummy coded som ja nej ift et stillet spørgsmål. Da lederen kun har svaret 1 i abs_5 og 0 i alle andre kan vi altså bare her beholde abs_5, og sige at det er på en 1-5 skala hvor 1 er slet ikke, 5 er hele tiden. 


##### combining leader data w all data 
```{r}
# fixing the names in leader variable
colnames(leader_long_df) <- paste("lead", colnames(leader_long_df), sep = "_")

leader_long_df <- leader_long_df %>% 
  rename(Day = lead_Day, 
         SurveyID = lead_SurveyID)

# merging both
lead_employee_all_data <- merge(final_clean_long_merged, leader_long_df, by = c("Day" = "Day", "SurveyID" = "SurveyID"), all = TRUE)

df_huge <- lead_employee_all_data %>% 
  select(Day, SurveyID, Absense_Score, present_Score, age, gen, ten_1, sat_Score, s6_Score, wb_hap_Score, wb_he_Score, wb_so_Score, ls1_Score,ls2_Score,ls3_Score, lead_wb_hap_Score, lead_wb_he_Score, lead_wb_so_Score, lead_es_1_Score, lead_es_2_Score, lead_es_3_Score, lead_present_Score, lead_present_Score, lead_abs5_score)

####### LOOPING TO FIX COLUMNS ####### 
# List of column names to process
columns_to_process <- c("sat_Score", "wb_hap_Score", "wb_he_Score", "wb_so_Score", "ls1_Score","ls2_Score","ls3_Score", "lead_wb_hap_Score", "lead_wb_he_Score", "lead_wb_so_Score", "lead_es_1_Score", "lead_es_2_Score", "lead_es_3_Score", "lead_present_Score", "lead_present_Score", "lead_abs5_score")

# Loop through each column and apply the condition
for (col in columns_to_process) {
  df_huge[[paste0("fix_", col)]] <- ifelse(df_huge[[col]] > 10, NA, df_huge[[col]])
}

```

```{r}
test_mod <- lmer(fix_wb_he_Score ~ lead_wb_he_Score +age + gen + ten_1 + Day +  (Day + 1 | SurveyID), data = df_huge)
```










