---
title: "count data"
author: "LAURA PAABY"
date: "2023-08-16"
output: html_document
---

```{r}
pacman::p_load(tidyverse)
```



# BIG DATA 
==> optælling af hvor mange respondenter vi har som har besvaret baseline OG diary study gennem hele perioden/det meste af perioden

```{r}
big_df <- read.csv("/Users/laura/Desktop/work_bss/data/all_data_merged.csv")

# List of column names to process
columns_to_process <- c("Absense_Score", "present_Score", "ls1_Score", "ls2_Score", "ls3_Score", "wb_he_Score", "wb_hap_Score", "wb_so_Score")

# Loop through each column and apply the condition
for (col in columns_to_process) {
  big_df[[paste0("fix_", col)]] <- ifelse(big_df[[col]] > 10, NA, big_df[[col]])
}

```


**Function to count:**
```{r}
count_participants <- function(variable_names, total_days_criteria) {

  # Filter out rows with missing survey data
  survey_data <- big_df %>%
    filter(!rowSums(is.na(select(., all_of(variable_names)))))
  
  # find all subjects present in this df 
  subjects_in_total <- length(unique(survey_data$SurveyID))

  # Count the number of days each subject has answered in the survey data
  subject_answered_days <- survey_data %>%
    group_by(SurveyID) %>%
    summarize(total_days = n_distinct(Day))

  # Filter subjects who have answered the specified number of days for all variables
  subjects_with_criteria <- subject_answered_days %>%
    filter(total_days >= total_days_criteria)

  # Count the number of subjects meeting the criteria
  num_subjects <- nrow(subjects_with_criteria)
  
  # find mean number of days 
  mean_days <- mean(subject_answered_days$total_days)
  
  return(c(subjects_in_total, num_subjects, mean_days))
}
```


Now using this function on selected variables looping through 30 days of observations: 

**All variables:**
```{r}
var_names_all <- c("fix_ls1_Score", "fix_ls2_Score", "fix_ls3_Score", "fix_present_Score", "fix_Absense_Score", "fix_wb_hap_Score", "fix_wb_he_Score", "fix_wb_so_Score")

count_participants(var_names, 9)
```

**absense thoughts, LS1, LS2 og LS3 **
```{r}
# Create an empty data frame to store the results
results_df_ABS_LS <- data.frame(Total_Days_Criteria = numeric(0),
                          Subjects_In_Total = numeric(0),
                          Num_Subjects = numeric(0),
                          Mean_Days = numeric(0))


# names of variables:
var_ABS_LS <- c("fix_ls1_Score", "fix_ls2_Score", "fix_ls3_Score", "fix_Absense_Score")

# Loop through total_days_criteria from 30 to 1
for (criteria in 30:1) {
  result <- count_participants(var_ABS_LS, criteria)
  subjects_in_total <- result[1]
  num_subjects <- result[2]
  mean_days <- result[3]
  
  # Append the results to the data frame
  results_df_ABS_LS <- rbind(results_df_ABS_LS, data.frame(Total_Days_Criteria = criteria,
                                              Subjects_In_Total = subjects_in_total,
                                              Num_Subjects = num_subjects,
                                              Mean_Days = mean_days))
  
}
```


**absense thoughts, wb_health, wb_social og wb_happy:**
```{r}
# Create an empty data frame to store the results
results_df_ABS_WB<- data.frame(Total_Days_Criteria = numeric(0),
                          Subjects_In_Total = numeric(0),
                          Num_Subjects = numeric(0),
                          Mean_Days = numeric(0))


# names of variables:
var_ABS_WB <- c("fix_Absense_Score", "fix_wb_hap_Score", "fix_wb_he_Score", "fix_wb_so_Score")

# Loop through total_days_criteria from 30 to 1
for (criteria in 30:1) {
  result <- count_participants(var_ABS_WB, criteria)
  subjects_in_total <- result[1]
  num_subjects <- result[2]
  mean_days <- result[3]
  
  # Append the results to the data frame
  results_df_ABS_WB <- rbind(results_df_ABS_WB, data.frame(Total_Days_Criteria = criteria,
                                              Subjects_In_Total = subjects_in_total,
                                              Num_Subjects = num_subjects,
                                              Mean_Days = mean_days))
}

```



**presenteeism, LS1, LS2 og LS3 **
```{r}
# Create an empty data frame to store the results
results_df_pres_LS <- data.frame(Total_Days_Criteria = numeric(0),
                          Subjects_In_Total = numeric(0),
                          Num_Subjects = numeric(0),
                          Mean_Days = numeric(0))


# names of variables:
var_pres_ls <- c("fix_ls1_Score", "fix_ls2_Score", "fix_ls3_Score", "fix_present_Score")

# Loop through total_days_criteria from 30 to 1
for (criteria in 30:1) {
  result <- count_participants(var_pres_ls, criteria)
  subjects_in_total <- result[1]
  num_subjects <- result[2]
  mean_days <- result[3]
  
  # Append the results to the data frame
  results_df_pres_LS <- rbind(results_df_pres_LS, data.frame(Total_Days_Criteria = criteria,
                                              Subjects_In_Total = subjects_in_total,
                                              Num_Subjects = num_subjects,
                                              Mean_Days = mean_days))
}

```


**presenteeism, wb_health, wb_social og wb_happy:**
```{r}
# Create an empty data frame to store the results
results_df_pres_WB <- data.frame(Total_Days_Criteria = numeric(0),
                          Subjects_In_Total = numeric(0),
                          Num_Subjects = numeric(0),
                          Mean_Days = numeric(0))


# names of variables:
var_pres_ls <- c("fix_wb_hap_Score", "fix_wb_he_Score", "fix_wb_so_Score", "fix_present_Score")

# Loop through total_days_criteria from 30 to 1
for (criteria in 30:1) {
  result <- count_participants(var_pres_ls, criteria)
  subjects_in_total <- result[1]
  num_subjects <- result[2]
  mean_days <- result[3]
  
  # Append the results to the data frame
  results_df_pres_WB <- rbind(results_df_pres_WB, data.frame(Total_Days_Criteria = criteria,
                                              Subjects_In_Total = subjects_in_total,
                                              Num_Subjects = num_subjects,
                                              Mean_Days = mean_days))
}

```



# Missing Data Analysis:
```{r}
pacman::p_load(finalfit, misty,BaylorEdPsych)
```


```{r}
mis_dat <- big_df %>% 
  select(Day, SurveyID, Absense_Score, ls1_Score, ls2_Score,ls3_Score, wb_so_Score, wb_hap_Score, wb_he_Score, present_Score, s6_Score, sat_Score, Contact_Score)

mis_dat[mis_dat == 99] <- NA

mis_dat %>% 
  missing_plot()
```

```{r}
little_test <- na.test(mis_dat, digits = 2, p.digits = 10, as.na = NULL, check = TRUE, output = TRUE)

little_test$result
```
Given the high statistic value and low p-value, we can conclude that the data is not missing completely at random. 


https://cloud.r-project.org/web/packages/finalfit/vignettes/missing.html <- `mice` is the most common way to impute data, so that might be a way to go. 


### Data imputation
This is done for 99 and initial NAs 

Lets first look at the missing data:
```{r}
pacman::p_load(mice, VIM)
md_pat <- md.pattern(mis_dat)

aggr_plot <- aggr(mis_dat, col=c('navyblue','red'), numbers=TRUE, sortVars=TRUE, labels=names(data), cex.axis=.7, gap=3, ylab=c("Histogram of missing data","Pattern"))
```


```{r}
tempData <- mice(mis_dat,m=5,maxit=50,meth='pmm',seed=500)
summary(tempData)


stripplot(tempData, pch = 20, cex = 1.2)

```
making all cols numeric to make them imputable by another methods 
```{r}
df_mis <- mis_dat
columns_to_convert <- c("ls1_Score", "ls2_Score", "ls3_Score", "Absense_Score", "wb_so_Score", "wb_hap_Score", "wb_he_Score", "present_Score", "s6_Score", "sat_Score", "Contact_Score")

for (col in columns_to_convert) {
  df_mis[[col]] <- as.factor(df_mis[[col]])
}

#df_mis[df_mis == 98] <- "A"
#df_mis[df_mis == 97] <- "B"
#df_mis[df_mis == 96] <- "C"

##### NOW TRYING DIFFERENT IMPUTATION METHODS: 
tempData1 <- mice(df_mis,m=5,maxit=50,meth='polyreg',seed=500)

tempData2 <- mice(df_mis,m=3,maxit=10,meth='polr',seed=20) #### DEN HER ER BEDST

```

*I use the polyreg method, as we are dealing with ordinal data. *

```{r}
df_mis %>% 
  group_by(Day) %>% 
  count()

```


```{r}
#### choosing a final DF 
completedData2 <- complete(tempData2,2)


#### Inspecting the initial distribution versus the imputed:
df_mis %>% 
  group_by(ls1_Score)


completedData2 %>% 
  group_by("ls1_Score") %>% 
  count()

imputed_survey_dat <- completedData2
write_csv(imputed_survey_dat, "/Users/laura/Desktop/work_bss/data/imputed_survey_dat.csv")
```





# Power analysis 

```{r}
# Check if R packages are installed

list.of.packages = c("htmltools","shiny","htmltools","shiny","DT","nlme","ggplot2","gridExtra",
"data.table","plyr","dplyr","formattable","tidyr","MASS","shinyjs","compiler","future.apply","devtools")
new.packages = list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

library(htmltools)
library(shiny)
library(DT)
library(nlme)
library(ggplot2)
library(gridExtra)
library(data.table)
library(plyr)
library(dplyr)
library(formattable)
library(tidyr)
library(MASS)
library(shinyjs)
library(compiler)
library(future.apply)

library(devtools)
devtools::install_github("ginettelafit/PowerAnalysisIL", force = T)

library(PowerAnalysisIL)

# Using Gist: users can launch this app with:
shiny::runGist('6bac9d35c2521cc4fd91ce4b82490236')

```









