---
title: "MODEL TESTS"
author: "LAURA PAABY"
date: "2023-05-08"
output: html_document
---

```{r}
pacman::p_load(tidyverse, readxl, ggplot2, lme4, psych, jtools, modelsummary)
```



# MODEL insight ;) 
*(1|participant ID)* =random effect (gives an individual intercept for each person)
      - doing this we model these individual differences by assuming different random *intercepts* for each subject. 
      In the words of the handbook: (1|Subject) specifies that level-1 observations are grouped by the level-2 variable called subject.
      
*(1 + Time | ID)* corresponds to random intercept and the random slope - so it assumes that each individual have a their own slope at each point in time.  
    

*(1|day)* = random effect (gives an unique intercept for each Day)
      - Make sense cause people's response could vary from Day to Day

Adding random effects, just think *"what can affect the outcome variable?"*
epsilon = error (represent the deviations from our predictions due to “random” factors that we cannot control experimentally.)

**Levels:**
three-level model if we consider the repeated assessments (level 1) as nested within days (level 2) which in turn are nested within subjects (level 3)



der er pt. convergence probs ved de her models: (1 + Time | ID), prøv at fjerne NA 

## ABS + SATISFACTION 
```{r}
df_abs_sat <- read_csv("/Users/laura/Desktop/work_bss/data/sat_abs_data.csv")

df_abs_sat$Day <- as.factor(df_abs_sat$Day)
df_abs_sat$SurveyID <- as.factor(df_abs_sat$SurveyID)

df_abs_sat_no_na <- df_abs_sat %>% 
  filter(!(is.na(fix_abs_score) == TRUE) | !(is.na(fix_sat_score) == TRUE))

df_abs_sat_no_na$Day <- as.numeric(df_abs_sat_no_na$Day)
```


##### models 
https://rpsychologist.com/r-guide-longitudinal-lme-lmer
```{r}
### RANDOM INTERCEPT FOR SUBJECTS ONLY 
mod1 <- lmer(fix_abs_score ~ fix_sat_score + age + gen + ten_1 + (1|SurveyID), data = df_abs_sat_no_na) 

### RANDOM INTERCEPT FOR SUBJECTS + DAY AS FIXED EFFECTS 
mod1_1 <- lmer(fix_abs_score ~ fix_sat_score + age + gen + ten_1 + Day + (1 |SurveyID), data = df_abs_sat_no_na) 

### Random slope for day, no random intercept
mod1_2 <- lmer(fix_abs_score ~ fix_sat_score + age + gen + ten_1 + (0 + Day|SurveyID), data = df_abs_sat_no_na) 
mod1_3 <- lmer(fix_abs_score ~ fix_sat_score + age + gen + ten_1 + Day + (0 + Day|SurveyID), data = df_abs_sat_no_na) 
mod1_4 <- lmer(fix_abs_score ~ fix_sat_score:Day + age + gen + ten_1 + Day + (0 + Day|SurveyID), data = df_abs_sat_no_na) 

### RANDOM INTERCEPT + RANDOM SLOPE
mod2 <- lmer(fix_abs_score ~ fix_sat_score + age + gen + ten_1+ (1+Day|SurveyID), data = df_abs_sat_no_na) 

### RANDOM INTERCEPT + RANDOM SLOPE + DAY AS FIXED EFFECTS 
mod2_1 <- lmer(fix_abs_score ~ fix_sat_score + age + gen + ten_1 + Day + (1+Day|SurveyID), data = df_abs_sat_no_na) 


### CONDITIONAL GROW MODEL => Satisfaction are conditioned by day 
# With no random effect 
mod3 <- lmer(fix_abs_score ~ fix_sat_score:Day + age + gen + ten_1 + (1|SurveyID), data = df_abs_sat_no_na) 
# With random effect
mod3_1 <- lmer(fix_abs_score ~ f:Day + age + gen + ten_1 + (1+Day|SurveyID), data = df_abs_sat_no_na) 


### CONDITIONAL GROW MODEL, but dropping intercept-slope covariance
# with day as fixed effect
mod4 <- lmer(fix_abs_score ~ fix_sat_score + age + gen + ten_1 + Day + (Day||SurveyID), data = df_abs_sat_no_na) 
# with day as conditional on sat 
mod4_1 <- lmer(fix_abs_score ~ fix_sat_score:Day + age + gen + ten_1 + (Day||SurveyID), data = df_abs_sat_no_na) 

# Level 2 fixed effects
mod5 <- lmer(fix_abs_score ~ fix_sat_score:Day + Day + fix_sat_score + age + gen + ten_1 + (1|SurveyID), data = df_abs_sat_no_na) 
mod5_1 <- lmer(fix_abs_score ~ fix_sat_score:Day + Day +fix_sat_score + age + gen + ten_1 + (1+Day|SurveyID), data = df_abs_sat_no_na)

```


```{r}
### finding the best model:
anova(mod1, mod1_2)
```



```{r}
modelsummary(mod1, stars = TRUE)
summ(mod1, exp = T) # use to get p values and pretty output 
summary(mod1_2)
```



## LS + ABS
```{r}
ls_mod_dat <- read_csv("/Users/laura/Desktop/work_bss/data/ls_pres_abs_data.csv")
head(ls_mod_dat)

ls_mod_dat_no_na <- ls_mod_dat %>% 
  filter(!(is.na(fix_abs_score) == TRUE) | !(is.na(fix_ls1_score) == TRUE) | !(is.na(fix_ls2_score) == TRUE) | !(is.na(fix_ls3_score) == TRUE))

ls_mod_dat_no_na$Day <- as.numeric(ls_mod_dat_no_na$Day)
```


#### correlation 
```{r}
# Selecting out the independent variables "X".
cor_dat_ls <- ls_mod_dat_no_na %>% 
  select(fix_ls1_score, fix_ls2_score, fix_ls3_score, age, ten_1)

# using pairs.panel() to look at the data
pairs.panels(cor_dat_ls, lm=T)
###### runs correlation covariance test ==> lm = true means it runs a linear model 

corr.test(cor_dat_ls$fix_ls1_score, cor_dat_ls$fix_ls2_score)
```


#### models 
```{r}
### RANDOM INTERCEPT FOR SUBJECT ONLY 
ls_mod1 <- lmer(fix_abs_score ~ fix_ls1_score + fix_ls2_score + fix_ls3_score + age + gen + ten_1 + (1 |SurveyID), data = ls_mod_dat_no_na)
# W day as fixed effect
ls_mod1_1 <- lmer(fix_abs_score ~ fix_ls1_score + fix_ls2_score + fix_ls3_score + age + gen + ten_1 + Day + (1 |SurveyID), data = ls_mod_dat_no_na) 


### RANDOM SLOPE AND INTERCEPT 
ls_mod2 <- lmer(fix_abs_score ~ fix_ls1_score + fix_ls2_score + fix_ls3_score + age + gen + ten_1 + (1 + Day|SurveyID), data = ls_mod_dat_no_na)

# + day as fixed 
ls_mod2_2 <- lmer(fix_abs_score ~ fix_ls1_score + fix_ls2_score + fix_ls3_score + age + gen + ten_1 + Day + (1 + Day|SurveyID), data = ls_mod_dat_no_na)

# + day as interaction (conditioning) 
ls_mod2_3 <- lmer(fix_abs_score ~ fix_ls1_score:Day + fix_ls2_score:Day + fix_ls3_score:Day + fix_ls1_score + fix_ls2_score + fix_ls3_score + age + gen + ten_1 + Day + (1 + Day|SurveyID), data = ls_mod_dat_no_na)


### 0 Covariance and fixed 
ls_mod3 <- lmer(fix_abs_score ~ fix_ls1_score + fix_ls2_score + fix_ls3_score + age + gen + ten_1 + Day + (Day||SurveyID), data = ls_mod_dat_no_na)
# w interaction 
ls_mod3_1 <- lmer(fix_abs_score ~ fix_ls1_score:Day + fix_ls2_score:Day + fix_ls3_score:Day + age + gen + ten_1 + fix_ls1_score + fix_ls2_score + fix_ls3_score + Day + (Day||SurveyID), data = ls_mod_dat_no_na)




#### ONLY SLOPE !!!!
### Random slope for day, no random intercept
mod4_1 <- lmer(fix_abs_score ~ fix_ls1_score + fix_ls2_score + fix_ls3_score + age + gen + ten_1 + (0 + Day|SurveyID), data = ls_mod_dat_no_na) 
mod4_2 <- lmer(fix_abs_score ~ fix_ls1_score + fix_ls2_score + fix_ls3_score + age + gen + ten_1 + Day + (0 + Day|SurveyID), data = ls_mod_dat_no_na) 

mod4_3 <- lmer(fix_abs_score:Day ~ fix_ls1_score + fix_ls2_score + fix_ls3_score + fix_ls1_score:Day + fix_ls2_score:Day + fix_ls3_score:Day + age + gen + ten_1 + Day + (0 + Day|SurveyID), data = ls_mod_dat_no_na) 
```


```{r}
anova(ls_mod1, mod4_1)

modelsummary(ls_mod1)
summary(mod4_1)
```



```{r}
summ(ls_mod3, exp = T)
```


#### ICC
Example - `ls_mod4`:
The ICC of 0.66 means that 66% of the variability in the outcome can be accounted for by the clustering structure of the data, in our case to between- subject differences.

Therefore, by using multilevel models we can better model the variation in the outcome by allowing for individual differences, in comparison to a model that does not take into account the multilevel structure of the data.


### averaged ls
```{r}
ls_mod_dat1 <- ls_mod_dat %>% 
  group_by(Day, SurveyID, age, gen, ten_1, fix_abs_score) %>% 
  summarise(mean_ls = mean(c(fix_ls1_score, fix_ls2_score, fix_ls3_score)))
```


```{r}
mod1 <- lmer(fix_abs_score ~ mean_ls + age + gen + ten_1 + (1|SurveyID), data = ls_mod_dat1) 

### RANDOM INTERCEPT FOR SUBJECTS + DAY AS FIXED EFFECTS 
mod1_1 <- lmer(fix_abs_score ~ mean_ls + age + gen + ten_1 + Day + (1 |SurveyID), data = ls_mod_dat1) 

### Random slope for day, no random intercept
mod1_2 <- lmer(fix_abs_score ~ mean_ls + age + gen + ten_1 + (0 + Day|SurveyID), data = ls_mod_dat1) 
mod1_3 <- lmer(fix_abs_score ~ mean_ls + age + gen + ten_1 + Day + (0 + Day|SurveyID), data = ls_mod_dat1) 
mod1_4 <- lmer(fix_abs_score ~ mean_ls:Day + age + gen + ten_1 + Day + (0 + Day|SurveyID), data = ls_mod_dat1) 

### RANDOM INTERCEPT + RANDOM SLOPE
mod2 <- lmer(fix_abs_score ~ mean_ls + age + gen + ten_1+ (1+Day|SurveyID), data = ls_mod_dat1) 

### RANDOM INTERCEPT + RANDOM SLOPE + DAY AS FIXED EFFECTS 
mod2_1 <- lmer(fix_abs_score ~ mean_ls + age + gen + ten_1 + Day + (1+Day|SurveyID), data = ls_mod_dat1) 


### CONDITIONAL GROW MODEL => Satisfaction are conditioned by day 
# With no random effect 
mod3 <- lmer(fix_abs_score ~ mean_ls:Day + age + gen + ten_1 + (1|SurveyID), data = ls_mod_dat1) 
# With random effect
mod3_1 <- lmer(fix_abs_score ~ mean_ls:Day + age + gen + ten_1 + (1+Day|SurveyID), data = ls_mod_dat1) 


### CONDITIONAL GROW MODEL, but dropping intercept-slope covariance
# with day as fixed effect
mod4 <- lmer(fix_abs_score ~ mean_ls + age + gen + ten_1 + Day + (Day||SurveyID), data = ls_mod_dat1) 
# with day as conditional on sat 
mod4_1 <- lmer(fix_abs_score ~ mean_ls:Day + age + gen + ten_1 + (Day||SurveyID), data = ls_mod_dat1) 

# Level 2 fixed effects
mod5 <- lmer(fix_abs_score ~ mean_ls:Day + Day + mean_ls + age + gen + ten_1 + (1|SurveyID), data = ls_mod_dat1) 
mod5_1 <- lmer(fix_abs_score ~ mean_ls:Day + Day +mean_ls + age + gen + ten_1 + (1+Day|SurveyID), data = ls_mod_dat1)
```
```{r}
anova(mod1, mod1_2)

modelsummary(mod1)
summary(mod1)
```


# WB + ABS 
Does wellbeing affect your reported absenteeism?



https://rpubs.com/mhanauer/305316



