---
title: "timelag models"
author: "LAURA PAABY"
date: "2023-08-15"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
pacman::p_load(tidyverse, readxl, lme4)

big_df <- read.csv("/Users/laura/Desktop/work_bss/data/all_data_merged.csv")

# List of column names to process
columns_to_process <- c("Absense_Score", "present_Score", "ls1_Score", "ls2_Score", "ls3_Score", "wb_he_Score", "wb_hap_Score", "wb_so_Score")

# Loop through each column and apply the condition
for (col in columns_to_process) {
  big_df[[paste0("fix_", col)]] <- ifelse(big_df[[col]] > 10, NA, big_df[[col]])
}

my_dat <- big_df %>% 
  select(SurveyID, Day, fix_Absense_Score, fix_present_Score, age, gen, ten_1, fix_ls1_Score, fix_ls2_Score, fix_ls3_Score, fix_wb_he_Score, fix_wb_hap_Score, fix_wb_so_Score)

```


# Data prep


## *one day delay* 
#### absenteeism 
Fix data to answer:
  H2: Daily social support from leader is negatively related to followers’ daily absenteeism the following day.

```{r}

# making new columns 
abs_delay_dat <- my_dat %>%
  arrange(SurveyID, Day) %>%
  group_by(SurveyID) %>%
  mutate(next_day = lead(Day),
         ABS_observation_next_day = lead(fix_Absense_Score),
         days_in_between = lead(Day) - Day)

```



modellos:
```{r}
abs_mod <- lmer(ABS_observation_next_day ~ fix_ls1_score + fix_ls2_score + fix_ls3_score  + gen + age +  ten_1 + Day + days_in_between + (SurveyID + 1 | Day), data = abs_delay_dat)

summary(abs_mod)
```


#### presenteeism 
Fix data to answer:
  H1: Daily social support from leader is negatively related to followers’ presenteeism the following day. 

```{r}
# making new columns 
pres_delay_dat <- my_dat %>%
  arrange(SurveyID, Day) %>%
  group_by(SurveyID) %>%
  mutate(next_day = lead(Day),
         PRES_observation_next_day = lead(fix_present_Score),
         days_in_between = lead(Day) - Day)

```



modellos:
```{r}
pres_day_mod <- glmer(as.factor(observation_next_day) ~ fix_ls1_score + fix_ls2_score + fix_ls3_score  + gen + age +  ten_1 + Day + days_in_between + (SurveyID + 1 | Day), data = pres_delay_dat, family = "binomial")

summary(pres_day_mod)
```
  


  
## *one week delay* 
Here we are interested in seeing if the previous weeks support and well-being is related to the current weeks absenteeism and presenteeism assessments. 


```{r}
# lets make the week variable
my_dat$week <- ifelse(my_dat$Day %in% c(1:7), 1, ifelse(my_dat$Day %in% c(8:14), 2, ifelse(my_dat$Day %in% c(15:21), 3, ifelse(my_dat$Day %in% c(22:28), 4, NA))))

```


#### presenteeism 
Now looking at *presenteeism*:
```{r}
pres_weekly <- my_dat %>% 
  select(week, Day, SurveyID, fix_ls1_Score, fix_ls2_Score, fix_ls3_Score, fix_present_Score, fix_wb_hap_Score, fix_wb_he_Score, fix_wb_so_Score, gen, age, ten_1)

pres_weekly$present_Score_dummy <- ifelse(pres_weekly$fix_present_Score == 1, 0, ifelse(pres_weekly$fix_present_Score == 2, 1, NA))
```


```{r}
# Calculate the proportion of 1's and 0's for each subject
summary_pres_data <- pres_weekly %>%
  group_by(SurveyID, week) %>%
  summarize(count_1 = sum(!is.na(present_Score_dummy) & present_Score_dummy == 1),
          count_0 = sum(!is.na(present_Score_dummy) & present_Score_dummy == 0),
          total_responses = sum(!is.na(present_Score_dummy))) %>%
  mutate(prop_1 = count_1 / total_responses,
         prop_0 = count_0 / total_responses) %>%
  ungroup()

summary_data


#### merging it with original 
merged_data_pres <- pres_weekly %>%
  left_join(summary_pres_data, by = c("SurveyID", "week"))
```


```{r}
# long format to plot: 
pres_prob_logn <- summary_pres_data %>%
  pivot_longer(cols = c(prop_1, prop_0), values_to = "prop") %>% 
  rename(pres_score_prop = name) %>% 
  filter(SurveyID %in% c(297,129,300))

pres_prob_logn$prop_no <- ifelse(pres_prob_logn$pres_score_prop == "prop_1", 1, ifelse(pres_prob_logn$pres_score_prop == "prop_0",0, NA))

pres_prob_logn %>% 
  mutate(`Reported Presenteeism` = as.factor(prop_no)) %>% 
  ggplot(aes(week, prop, fill = `Reported Presenteeism`)) +
  geom_bar(stat = "identity", position = "stack") +
  facet_grid(~SurveyID) +
  theme_bw() +
  labs(x = "Week", y = "Proportions of Reported Presenteeism", title = "Three Subjects Proportional Weekly Reporting of Presenteeism")
  
```

#### absenteeism  
Now looking at *absenteeism*:

```{r}
abs_weekly <- my_dat %>% 
  select(week,Day, SurveyID, fix_ls1_Score, fix_ls2_Score, fix_ls3_Score, fix_Absense_Score, fix_wb_hap_Score, fix_wb_he_Score, fix_wb_so_Score, gen, age, ten_1)

```


```{r}
# Calculate the proportion of 1's and 0's for each subject
summary_abs_data <- abs_weekly %>%
  group_by(SurveyID, week) %>%
  summarize(count_1 = sum(!is.na(fix_Absense_Score) & fix_Absense_Score == 1),
          count_2 = sum(!is.na(fix_Absense_Score) & fix_Absense_Score == 2),
          count_3 = sum(!is.na(fix_Absense_Score) & fix_Absense_Score == 3),
          count_4 = sum(!is.na(fix_Absense_Score) & fix_Absense_Score == 4),
          count_5 = sum(!is.na(fix_Absense_Score) & fix_Absense_Score == 5),
          total_responses = sum(!is.na(fix_Absense_Score))) %>%
  mutate(prop_1 = count_1 / total_responses,
         prop_2 = count_2 / total_responses,
         prop_3 = count_3 / total_responses,
         prop_4 = count_4 / total_responses,
         prop_5 = count_5 / total_responses) %>%
  ungroup()

merged_data_abs <- abs_weekly %>%
  left_join(summary_abs_data, by = c("SurveyID", "week"))
```


```{r}
# long format to plot: 
abs_prob_logn <- summary_abs_data %>%
  pivot_longer(cols = c(prop_1, prop_2, prop_3, prop_4, prop_5), values_to = "prop") %>% 
  rename(abs_score_prop = name) %>% 
  filter(SurveyID %in% c(297,129,300))

abs_prob_logn$prop_no <- ifelse(abs_prob_logn$abs_score_prop == "prop_1", 1, ifelse(abs_prob_logn$abs_score_prop == "prop_2",2, ifelse(abs_prob_logn$abs_score_prop == "prop_3", 3, ifelse(abs_prob_logn$abs_score_prop == "prop_4", 4, ifelse(abs_prob_logn$abs_score_prop == "prop_5", 5, NA)))))

abs_prob_logn %>% 
  mutate(`Reported Absense Thoughts` = as.factor(prop_no)) %>% 
  ggplot(aes(week, prop, fill = `Reported Absense Thoughts`)) +
  geom_bar(stat = "identity", position = "stack") +
  facet_grid(~SurveyID) +
  theme_bw() +
  labs(x = "Week", y = "Proportions of Reported Absense Thoughts", title = "Three Subjects Proportional Weekly Reporting of Absense Thoughts")
  
```





